The mass relations between supermassive black holes and their host galaxies at $1< z<2$ with \hst-WFC3

### 2019-06-18 manuscript/manuscript.tex
Before git pull on overleaf from TT

\subsection{Target selection}

@@

Across the intermediate redshift sample, we recalibrate the \mbh\ by \halpha\ or \hbeta\ using the self-consistent recipes introduced in Section~\ref{mbh}. For \mbh\ estimated by \Mgii\, we adopt the recipe by \citet{Ding2017b} to recalibrate them.
}

@@

%Introduce the final inference using fitting:
The host properties of one AGN system is inferred via the following steps. First, we model the AGN and host using each PSFs in the library. Inputting the fitting ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that, the \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC. In our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow. Thus, we only take the best-fit inference using PSO for the further calculations.}.
To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff\ $\in[0\farcs{}1,1\farcs{0}]$, and \sersic\ index $n\in[1,7]$\footnote{{\color{blue}
%As will see, three AGN systems would have finally inference with abnormally high \sersic\ index value (i.e., $n>5$). We test to reanalyze these sample and fix the \sersic\ index within $n\in[1,4]$ and find their results changes very little ---  $\Delta$\lhost\ and $\Delta$\smass\ within 0.1 dex.
We test to use $n\in[1,4]$ as prior to fit the systemic with high \sersic\ index ($n>4.5$), and find that the changes on the inference of their host magnitude are very limited ($<0.03$ dex).}
}.
Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best fit PSFs. We infer the host \sersic\ parameters (i.e., host flux, \Reff, \sersic\ index) using a weighted arithmetic mean. The weight is calculated by:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter so that when $i=8$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2,
\end{eqnarray} 
The goal of this recipe is to weight each PSF based on their relative goodness of fit, while ensuring at least eight are used to capture the range of systematic uncertainties. The answers would not change significantly if we had chosen a different number of PSFs, as we show below.

@@

In Figure~\ref{fig:AGN_decomp}, we demonstrate the optimized results inferred by \lenstronomy, including the AGN images, best-fit models, image subtract point source (i.e. host) and the residuals, taking COSMOS-CID1174 as an example. The weights adopted in the analysis are listed in Table~\ref{tab:weight_CID1174}. In order to quickly overview our inference, we summarize the relations of the properties between effective radius \Reff, 2) \sersic\ index and 3) host to total flux ratio in Figure~\ref{fig:flux_r_n_corner}. We also comparing the distribution of the \sersic\ values to the inactive galaxies in the Appendix~\ref{sec:comp_inactive}.

@@

The inference of the host properties is weighted by eight top-ranked PSFs. The smaller volume of top-ranked  PSFs would possibly underestimate the uncertainties of the inference. To understand how the choice of the number of top-ranked PSF affects our inference, we compare to the inference by using five and ten top-ranked PSFs. As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference has been solid when the amount of selected PSF exceeds five.

@@

\subsection{Host galaxy properties}
We derive the rest-frame R band magnitude ($M_R$) and luminosity ($L_R$) of our sample based on their filter magnitude. 18/32 systems have multi-band host magnitude which enables us to select the best stellar population that could fit the overall sample. We find that the 1~Gyrs stellar population with solar metallicity by Chabrier initial mass function (IMF)~\citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these samples.

Adopting the color information, we perform the K-correction and derive the rest-frame R band magnitude of our sample. Given that the WFC3 filter we selected is very close to the rest-frame R band, we expect the $M_R$ uncertainty introduced by this K-correction is within 0.05~mag. We derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$~\citep{Blanton07}.

Taking the stellar population, we estimate the stellar mass content of each host galaxy according to the mass-to-light ratio of the stellar population we adopted. The uncertainty level associated with the stellar mass is expected to be of order 0.1~dex, at fixed stellar initial mass function (changing the initial mass function would change all our stellar masses systematically).

The inferred $L_R$ and $M_*$ are listed in Table~\ref{tab:result_sersic}. In the rest of this section, we compare their relations to the \mbh.

\subsection{\mbh-\lhost\ relation}\label{sec:ml}
We show our measurements of the \mbh-\lhost\ relation together with the comparison sample in Figure~\ref{fig:ML}. Following common practice, we fit the local relation as a linear relation,
\begin{eqnarray}
\label{eq:MLlocal}
\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{L_R}{10^{10}L_{\odot}}),
\end {eqnarray}
which enables direct comparison to the distant sample. The inferred local relations, as presented in the Figure~\ref{fig:ML}, shows that the observed \mbh-\lhost\ relation for our measurements is nearly identical to the local and intermediate ones. The observational result indicates that the relation between black hole mass and the host luminosity are similar at different period of the universe.

@@

@@

\subsection{\mbh-\smass\ relation}\label{sec:mm}
In Figure~\ref{fig:MM}, we plot the \mbh-\smass\ relation and compare to the local and intermediate sample. We visually see that the relations for the three samples are close from one to another. Similar as Equation~\ref{eq:MLlocal}, we consider the local \mbh-\smass\ relations as linear relation as:
\begin{eqnarray}
\label{eq:MMlocal}
\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{M_*}{10^{10}M_{\odot}}).
\end {eqnarray}

To understand the evolution for high-$z$ relations, we fit the offset as a function of redshift in form as:
\begin{eqnarray}
\label{eq:offset}
\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z),
\end{eqnarray} 
where $\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$. We obtain $\gamma  = 0.74 \pm 0.21$, i.e. tentative evidence for evolution, see Figure~\ref{fig:MM-vz}, panel (a). We also show the ratio of \mbh-\smass\ of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b).

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style1.pdf}}&
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style0.pdf}}\\
\end{tabular}
\caption{\label{fig:MM-vz} 
Left: illustration of the offset in log\mbh\ (VS. \smass) as a function of redshift. The orange band is the intrinsic scatter of local linear relation. Right: \mbh/\smass\ as a function of redshift. 
{\color{blue} We use green open circles to show the expected shifting of the median value of the $\Delta$\mbh\ before and after consider the selection effect using framework by \citet{Schulze2011} in Section~\ref{sec:sf_framework}.}
{\color{red} [Xuheng: The blue points are from Cisternas et al. 2011, they are consistent to the local ones.]}
}
\end{figure*}

We visually see that in Figure~\ref{fig:MM-vz}, panel (a), most of our measurements locate within the scattering range of the local sample. We doubt whether the positivity of $\gamma$ stems from the three outliers (i.e., the top-three systems in Figure~\ref{fig:MM}). We thus exclude these systems and re-run the statistical analysis to see if offset still exists among the rest of our sample. As a result, we obtain that $\gamma  = 0.55 \pm 0.29$, indicating the positive evolution trend become weaker but still exists, as shown in Figure~\ref{fig:MM_restsample}.

\begin{figure}
\centering
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_subsample.pdf}}
\caption{\label{fig:MM_restsample} 
Same as Figure~\ref{fig:MM-vz}, left, but excluding the 3 outliers systems. The result shows the evolution still exist among the other 29 AGN sample.
}
\end{figure}

It is worth note that the local sample employed are bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses. That is, we are comparing the \mbh-\smass$_{,total}$ at the distant universe to the \mbh-\smass$_{,bulge}$ at today. Considering that a major part of the distant systems has indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{,bluge}$ of them are supposed to be even less.

Without taking into account the selection effect, the direct comparison shows that the growth of the black hole predates that of the host bulge.

\subsection{Selection effect}
\label{select_eff}

Our AGN sample is selected based on the value of \mbh, Eddington ratio, and \halpha\ broad emission line, with low nuclear-to-host ratios. The inference could be biased, when extending the selected sample to the global without properly considering the selection effect~\citep{Tre++07, Bennert++2011, Schulze2014, Park15}. In theory, the simulations~\citep{DeG++15} also find the scaling relations by the selected sample has steeper feature than the random ones, highlighting the necessity of eliminating the selection biases. {\color{blue} We consider the selection effect using two independent approach introduced in the following two subsections.

\subsubsection{Test selection effect using Monte Carlo simulation}
We take selection effects into account using the Monte Carlo simulation based on the approach introduced by \citet{Tre++07}. Following \citet{Park15, Ding2017b}, we generate the simulating samples from a combination of the local active \mbh\ function by \cite{Schulze2010} and the local samples adopted in this work. We then added Gaussian random noise to the simulated samples as a function of two free parameters, $\gamma$ and \sint, where \sint\ is the intrinsic scatter when considering the scaling relation as linear. According to the observed distribution, we consider the observational selection of \mbh\ of our samples by their lower and upper limits to model their distribution. To evaluate the posterior at the given $\gamma$ and \sint, for each object, we consider the likelihood of observing such object using the simulated sample, and consider whether the object would be selected or not, given the sensitivity. In addition, we adopt both uniform (flat) prior and lognormal prior for \sint\ (using the inference from linear fitting).

@@

\subsubsection{Test selection effect using Bayesian framework} \label{sec:sf_framework}
We use the Bayesian framework introduced by \citet{Schulze2011} to estimate the expected bias that could be raised by our selection window and local sample that adopted. Given the particular selection window (\mbh,  $L_{\rm bol}$ and Eddington ratio $\lambda$), the framework considers the fact that the intrinsic scatter in the BH-bulge relation has trend to decline regime of the stellar mass function, result in an average stellar masses lower than the relation. Moreover, the other relevant sources of bias are considered in this framework, for example the active fraction among SMBHs varies by the black hole mass function, in the sense that BHs with higher mass are less likely to be active than lower mass ones.

Considering our specific selection limits: $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$, we infer an expected bias of 0.21~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$. Interestingly, this bias could account for the offset that obtained in the \mbh-\smass\ correlations in Section~\ref{sec:mm}. We use green open circles to point out the shifting of the expected population given these biases, as shown in Figure~\ref{fig:MM-vz}.

Our conclusion is that the considering the selection effect using framework by \citet{Schulze2011}, we get consistent \mbh-\smass\ with the local sample.

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
\subfloat[\mbh-\lhost\ relation, evolution-corrected]
{\includegraphics[height=0.5\textwidth]{fig/MBH-L_ev.pdf}}&
\subfloat[offset in log\mbh\ (VS. \lhost) as a function of redshift]
{\includegraphics[height=0.5\textwidth]{fig/MBH-L-vz.pdf}}\\
\subfloat[\mbh-\lhost, flat prior]
{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_flatprior.pdf}}&
\subfloat[\mbh-\lhost, lognormal prior]
{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_lognormprior.pdf}}\\
\end{tabular}
\caption{\label{fig:ML-vz} 
Same as previous figures but for \mbh-\lhost relation, considering the passive evolution correction for host galaxy luminosity.}
\end{figure*}

{\color{blue}
\subsection{The origin of the offset}
{\color{red}[Xuheng:  Given their larger uncertainty, do we still want to present these figures?]}
We seek for the cause that could raise the evolution in the BH and host galaxy correlations at high redshift. We consider if the offset is related to the AGN activities. The straightforward way is to study such offset, i.e. $\Delta \log \mathcal M_{\rm BH}$, as a function of \mbh\ and Eddington ratios, showing in Figure~\ref{fig:offset_vs_MBH_edd}. Interestingly, we visually see the trend that the offset turns to be larger with at value of \mbh. However, at higher Eddington ratio, the offset turns to be lower.
 {\color{red} Some interpretations need to be presented.}

\begin{figure*}
\centering
\begin{tabular}{c c}
\subfloat[Offset of the \mbh-\smass\ relation as a function of \mbh.]
{\includegraphics[height=0.5\textwidth]{fig/offset_vs_MBH.pdf}}&
\subfloat[Offset of the \mbh-\smass\ relation as a function of Eddington ratio.]
{\includegraphics[height=0.5\textwidth]{fig/offset_vs_Edd.pdf}}\\
\end{tabular}
\caption{\label{fig:offset_vs_MBH_edd} 
Illustration of the offset for high-$z$ \mbh-\smass\ sample as a function of \mbh\ (left) and Eddington ratio (right).}
\end{figure*} 
}

@@

\subsection{Systematic with different local anchor}
To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011, H+R04}. In the literature, there are other local sample have been measured which also usually be considered as the local anchor. We note that different local samples have inconsistency which could change the result of the co-evolutions.

To estimate this effect, we compare our local \mbh-\smass\ sample to the local quiescent galaxies by \citet{Kormendy13} (hereafter K13). We find that K13's local \mbh-\smass\ relation would raise the anchor by $\sim$0.3~dex and totally erase the offset of $\Delta\log$\mbh. However, we also note that the \mbh-\sigstar\ relations in K13 is also higher than the one by our local sample. Note that the \mbh-\sigstar\ relations by the quiescent galaxy are usually used to determine the virial coefficient for AGNs. That is, adopting the K13 would boost the value of our \mbh\ by $\sim$0.3~dex as well. As a result, our inference of the fitted offset $\gamma$ still remains at the same level.

This quick comparison of the local sample highlights the need of the solid local baseline for the future studies (Bennert et al., in prep).

>>>>

\subsection{Target selection}\label{sec:target_selection}

@@

Across the intermediate redshift sample, we recalibrate the \mbh\ by \halpha/\hbeta\ emission line using the self-consistent recipes introduced in Section~\ref{mbh}. For \mbh\ estimated by \Mgii\, we adopt the recipe by \citet{Ding2017b} to recalibrate them.

\section{Expected selection effect bias} \label{sec:sf_framework}
Our AGN sample is selected based on the value of \mbh, Eddington ratio, and \halpha\ broad emission line, with low nuclear-to-host ratios It has been known that sample selection effects could influence the observed black hole-host relations and its evolution with redshift ~\citep{Schulze2011, Tre++07, Bennert++2011, Park15}. In theory, the simulations~\citep{DeG++15} also find the scaling relations by the selected sample has steeper feature than by the random ones. To highlight this influence, we study the expected bias of the \mbh\ given our target selection in Section~\ref{sec:target_selection}.

We use the Bayesian framework introduced by \citet{Schulze2011} to estimate the expected bias. Given our particular selection window (\mbh,  $L_{\rm bol}$ and Eddington ratio $\lambda$) and the local sample, the framework considers the fact that the intrinsic scatter in the BH-bulge relation has trend to decline regime of the stellar mass function, result in an average stellar masses lower than the relation. Moreover, the other relevant sources of bias are considered in this framework, for example the active fraction among SMBHs varies by the black hole mass function, in the sense that BHs with higher mass are less likely to be active than lower mass ones.

Adopting our specific selection limits into the framework (i.e., $\log($\mbh$)~\in[7.5, 8.56]$, $\log(L_{\rm bol}) \in [45.0, 46.2] $ and  $\log(\lambda) \in [-2.0, 0.5]$), we infer an expected bias of $+0.21$~dex in the observed $\Delta\log($\mbh$)$ for samples at $z\sim1.5$.

We would correct our inference by taking this select bias into account in the result sections.

%Interestingly, this bias could account for the offset that obtained in the \mbh-\smass\ correlations in Section~\ref{sec:mm}. We use green open circles to point out the shifting of the expected population given these biases, as shown in Figure~\ref{fig:MM-vz}.

%Our conclusion is that the considering the selection effect using framework by \citet{Schulze2011}, we get consistent \mbh-\smass\ with the local sample.
}

@@

%Introduce the final inference using fitting:
The host properties of one AGN system is inferred via the following steps. First, we model the AGN and host using each PSFs in the library. Inputting the fitting ingredients to \lenstronomy, the posterior distribution of the parameter space is calculated and optimized by adopting the Particle Swarm Optimizer (PSO)\footnote{Note that, the \lenstronomy\ enables one to further infer the parametric confidence interval using MCMC. In our case, given a fixed PSF, the $1-\sigma$ inference of each parameter are extremely narrow. Thus, we only take the best-fit inference using PSO for the further calculations.}.
To avoid any unphysical inferences, we set the upper and lower limit for the key parameters as effective radius \Reff\ $\in[0\farcs{}1,1\farcs{0}]$, and \sersic\ index $n\in[1,7]$.
Then, we rank the performance of each PSF based on the $\chi^2$ value and select the top-eight PSFs as representative of the best fit PSFs. We infer the host \sersic\ parameters (i.e., host flux, \Reff, \sersic\ index) using a weighted arithmetic mean. The weight is calculated by:
\begin{eqnarray}
\label{eq:weights}
w_i = exp \big(- \alpha \frac{ (\chi_i ^2 - \chi_{best} ^2 )}{2 \chi_{best} ^2} \big),
\end{eqnarray} 
where the $\alpha$ is an inflation parameter so that when $i=8$:
\begin{eqnarray}
\label{eq:alpha}
\alpha \frac{ \chi_{i=8} ^2 - \chi_{best} ^2 }{2 \chi_{best} ^2} = 2,
\end{eqnarray} 
The goal of this recipe is to weight each PSF based on their relative goodness of fit, while ensuring at least eight are used to capture the range of systematic uncertainties. The answers would not change significantly if we had chosen a different number of PSFs, as we show below.

@@

In Figure~\ref{fig:AGN_decomp}, we demonstrate the optimized results inferred by \lenstronomy, including the AGN images, best-fit models, image subtract point source (i.e. host) and the residuals, taking COSMOS-CID1174 as an example. The weights adopted in the analysis are listed in Table~\ref{tab:weight_CID1174}.

@@

We apply this approach to the overall AGN systems to infer the overall host galaxy information. To quickly overview, we plot the relations of the properties between effective radius (\Reff), \sersic\ index and host to total flux ratio in Figure~\ref{fig:flux_r_n_corner} and leave the detail descriptions in the next Section. We realize that the inference of the host properties is weighted by eight top-ranked PSFs. The smaller volume of top-ranked  PSFs would possibly underestimate the uncertainties of the inference. To understand how the choice of the number of top-ranked PSF affects our inference, we compare to the inference by using five and ten top-ranked PSFs. As shown in Figure~\ref{fig:hist_compare}, the results are very consistent, meaning that the host inference has been solid when the amount of selected PSF exceeds five.

@@

\subsection{Host galaxy properties}
In previous section, we carry out the AGN-host decomposition and derive the host galaxy \sersic\ properties of the overall sample, as shown in Figure~\ref{fig:hist_compare}. The optimized resulting images for each sample are presented in the figures in Appendix~\ref{sec:restsample}. Based on the third column of these resulting figures (i.e. the ``data-Point source'' stamps), we find that all the systems have shown the evidence for existence of the host galaxies. We also find that merger feature of the host galaxies are not strong, showing that our sample possibly not be dominated by the major merger.

The host-total flux ratio of the sample are varies from 10\% to 90\% (concentrated between 20\% to 50\%). The effective radius and \sersic\ index are randomly distributed within the prior, rather than biased on upper/lower side. The inferred \Reff\ of our sample are between $\sim$1-7 kpc (peaked at $\sim$2.2kpc). 15/32 systems have \sersic\ index $n<2$, indicating they are composed of disk+bulge components.  Five systems have high \sersic\ index ($n>4.5$); we use $n\in[1,4]$ as prior to re-fit these systems and find that the changes on the inference of their host luminosity are very limited ($<0.03$ dex).

We also comparing the distribution of the \sersic\ values to the inactive galaxies in the Appendix~\ref{sec:comp_inactive} and find that our high-$z$ AGN host have very similar distribution.

We calculate the rest-frame R band magnitude ($M_R$) of our sample based on their filter magnitude. 18/32 systems have multi-band host magnitude which enables us to select the best stellar population that could fit the overall sample. We find that the 1~Gyrs stellar population with solar metallicity by Chabrier initial mass function (IMF)~\citep{Bruzual2003} could well match the color between the WFC3 and ACS band magnitude of these samples.

\subsection{\mbh-\lhost\ relation}\label{sec:ml}
Adopting the 1~Gyrs stellar population, we perform the K-correction to derive the rest-frame R band magnitude of our sample. Given that the WFC3 filter we selected is very close to the rest-frame R band, we expect the $M_R$ uncertainty introduced by this K-correction is within 0.05~mag. We derive the rest-frame R band luminosity by $\log L_R/L_{R, \odot} = 0.4 (M_{R, \odot}-M_R)$, where $M_{R, \odot}=4.61$~\citep{Blanton07}. The inferred $L_R$ are ranged between $\log L_R \in [9.5, 11.5]$ ($L_{\odot,R}$), as summarized in Table~\ref{tab:result_sersic}.

We show our measurements of the \mbh-\lhost\ relation together with the comparison sample in Figure~\ref{fig:ML}. Following common practice, we fit the local relation as a linear relation,
\begin{eqnarray}
\label{eq:MLlocal}
\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{L_R}{10^{10}L_{\odot}}),
\end {eqnarray}
which enables direct comparison to the distant sample. The inferred local relations, as presented in the Figure~\ref{fig:ML}, shows that the observed \mbh-\lhost\ relation for our measurements is nearly identical to the local and intermediate ones. The observational result indicates that the relation between black hole mass and the host luminosity are similar at different period of the universe.

@@

We note three outlier measurements deviated from the distribution of overall sample, which are SXDS-X763, CDFS-1, CDFS-724. We expect that they could have abnormal host inference. Indeed, for SXDS-X763, the inferred host \Reff\ has large scatter ($\sim 75\%$) with the lowest host-total flux ratio in the overall sample ($<10\%$). For CDFS-1 and CDFS-724, their host are \Reff$<0\farcs{}15$, smaller than the PSF FWHM. Moreover, the broad emission line of \mbh\ are from \citet{Suh2015} which could have systemic to \citet{Schulze2018}. Thus, the measurements of these three systems have less fidelity.

@@

\subsection{\mbh-\smass\ relation}\label{sec:mm}

Taking the stellar population, we estimate the stellar mass content of each host galaxy according to the mass-to-light ratio of the stellar population we adopted. The uncertainty level associated with the stellar mass is expected to be of order 0.1~dex, at fixed stellar initial mass function (changing the initial mass function would change all our stellar masses systematically). The inferred $M_*$ are ranged between $\log M_* \in [9.7, 11.3]$ ($M_{\odot}$), listed in Table~\ref{tab:result_sersic}.

In Figure~\ref{fig:MM}, we plot the our \mbh-\smass\ measurements and compare to the local and intermediate sample. We visually see that the relations for the three samples are close. Similar as Equation~\ref{eq:MLlocal}, we consider the local \mbh-\smass\ relations as linear relation as:
\begin{eqnarray}
\label{eq:MMlocal}
\log \big( \frac{\mathcal M_{\rm BH}}{10^{7}M_{\odot}})= \alpha + \beta \log(\frac{M_*}{10^{10}M_{\odot}}).
\end {eqnarray}

To understand the evolution for high-$z$ relations, we fit the offset as a function of redshift in form as:
\begin{eqnarray}
\label{eq:offset}
\Delta \log \mathcal M_{\rm BH}= \gamma \log (1 + z),
\end{eqnarray} 
where $\Delta \log \mathcal M_{\rm BH} = \log \big( \frac{\mathcal M_{\rm  BH}}{10^{7}M_{\odot}}) -\alpha-\beta\log(\frac{M_*}{10^{10}M_{\odot}})$. We obtain $\gamma  = 0.84 \pm 0.26$, i.e. tentative evidence for evolution, see Figure~\ref{fig:MM-vz}, panel (a). We also show the ratio of \mbh-\smass\ of the three samples at different redshift in Figure~\ref{fig:MM-vz}, panel (b).

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style1.pdf}}&
{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_style0.pdf}}\\
\end{tabular}
\caption{\label{fig:MM-vz} 
Left: illustration of the offset in  $\log($\mbh$)$ (VS. \smass) as a function of redshift. The orange band is the intrinsic scatter of local linear relation. The red line and gray band are the best-fit and $1-\sigma$ offset fitting by Equation~\ref{eq:offset} using our 32 high-$z$ AGNs.
Right: \mbh/\smass\ as a function of redshift. 
We use green open circles to show the expected shifting of the median value of the $\Delta \log$\mbh\ before and after consider the selection effect using framework by \citet{Schulze2011} in Section~\ref{sec:sf_framework}.}
\end{figure*}

We visually see that in Figure~\ref{fig:MM-vz}, panel (a), most of our measurements locate within the scattering range of the local sample. We doubt whether the positivity of $\gamma$ stems from the three outliers discussed in last section. We thus exclude these outliers and re-run the statistical analysis to see if offset still exists. As a result, we obtain that $\gamma  = 0.65 \pm 0.27$, indicating the positive evolution trend become weaker but still exists.

%\begin{figure}
%\centering
%{\includegraphics[width=0.5\textwidth]{fig/MBH-Mstar-vz_subsample.pdf}}
%\caption{\label{fig:MM_restsample} 
%Same as Figure~\ref{fig:MM-vz}, left, but excluding the 3 outliers systems. The result shows the evolution still exist among the other 29 AGN sample.
%}
%\end{figure}

It is worth note that the local sample employed are bulge-dominated galaxies and the adopted \smass\ are equivalent to their bulge masses. That is, we are comparing the \mbh-\smass$_{,total}$ relations at the distant universe to the \mbh-\smass$_{,bulge}$ relations at local. Considering that a major part of the distant systems has indicated the disk component (i.e., the systems with fitted \sersic\ index close to 1), the \smass$_{, bluge}$ of them are supposed to be even less. Given that our 32 AGNs present the similar distribution to the inactive ones in CANDLES (see Appendix~\ref{sec:comp_inactive}), we expect the bulge-total ratio could be follow the similar ratio.

{\color{red}
[Xuheng will add one more section here, about the bulge \smass\ inference and the corresponding $\gamma$, after comparing to the CANDLES data.]
}

We summarize the inference of $\gamma$ using different combination of sample in Table~\ref{table:diff_sample_gam}. All the $\gamma$ by the observed \mbh-\smass\ are inferred as positive, indicating that the growth of the black hole predates that of the host bulge.

\begin{table}
\centering
    \caption{The inference of $\gamma$ using \mbh-\smass\ by different sample combination.}\label{table:diff_sample_gam}
     \resizebox{5.5cm}{!}{
     \begin{tabular}{cc}
     \hline
     Sample combination & $\gamma$ \\
     &\\
     \hline\hline
32 AGNs & 0.84$\pm$0.26\\    
29 AGNs (excluded outliers) & 0.65$\pm$0.27\\    
32 AGNs + intermediate &  0.62$\pm$0.20\\
     \hline
     \end{tabular}}
\tablecomments{These values are directly inference for the observation, which haven't yet taken the selection effect into account.}
\end{table}

\subsection{Selection effect}
\label{select_eff}
In Section~\ref{sec:sf_framework}, we adopt the Bayesian framework by \citet{Schulze2011} and find that there is an expected $+0.21$~dex bias in the inferred $\Delta \log$\mbh. Interestingly, this bias could account for the observed offset as obtained in the \mbh-\smass\ correlations in last Section. %~\ref{sec:mm}.
To make it clear, we use green open circles to point out the shifting of the expected population given these biases in Figure~\ref{fig:MM-vz}. We also show, in Figure~\ref{fig:offset_hist}, the histogram the $\Delta \log$\mbh\ by the high-$z$ sample and compare to the local ones. Clearly, the correction by considering this selection effect could almost mitigate the offset.
The result of the correction shows that the high-$z$ sample could have consistent \mbh-\smass$,_{\rm host}$ to the local sample.

\begin{figure}
\centering
{
\includegraphics[width=0.5\textwidth]{fig/hist_offset.pdf}
}
\caption{\label{fig:offset_hist} 
Illustration of the histogram of the $\log($\mbh$)$ offset for the local samples and 32 high-$z$ sample. The gray/red vertical line shows the median value of the offset for the high-$z$ sample, before/after considering the selection effect.}
\end{figure}

%Our conclusion is that the considering the selection effect using framework by \citet{Schulze2011}, we get consistent \mbh-\smass\ with the local sample.
Furthermore, we adopt an independent method to test the selection effect -- using the Monte Carlo simulation based on the approach introduced by \citet{Tre++07}. Following \citet{Park15, Ding2017b}, we generate the simulating samples from a combination of the local active \mbh\ function by \cite{Schulze2010} and the local samples adopted in this work. We then added Gaussian random noise to the simulated samples as a function of two free parameters, $\gamma$ and \sint, where \sint\ is the intrinsic scatter when considering the scaling relation as linear. According to the observed distribution, we consider the observational selection of \mbh\ of our samples by their lower and upper limits to model their distribution. To evaluate the posterior at the given $\gamma$ and \sint, for each object, we consider the likelihood of observing such object using the simulated sample, and consider whether the object would be selected or not, given the sensitivity. In addition, we adopt both uniform (flat) prior and lognormal prior for \sint\ (using the inference from linear fitting).

@@

@@

\begin{figure*}
\centering
\begin{tabular}{c c}
\subfloat[\mbh-\lhost\ relation, evolution-corrected]
{\includegraphics[height=0.5\textwidth]{fig/MBH-L_ev.pdf}}&
\subfloat[offset in  $\log($\mbh$)$ (VS. \lhost) as a function of redshift]
{\includegraphics[height=0.5\textwidth]{fig/MBH-L-vz.pdf}}\\
\subfloat[\mbh-\lhost, flat prior]
{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_flatprior.pdf}}&
\subfloat[\mbh-\lhost, lognormal prior]
{\includegraphics[width=0.5\textwidth]{fig/ML_MC_seleff_lognormprior.pdf}}\\
\end{tabular}
\caption{\label{fig:ML-vz} 
Same as previous figures but for \mbh-\lhost relation, considering the passive evolution correction for host galaxy luminosity.}
\end{figure*}

%{\color{blue}
%\subsection{The origin of the offset}
%{\color{red}[Xuheng:  Given their larger uncertainty, do we still want to present these figures?]}
%We seek for the cause that could raise the evolution in the BH and host galaxy correlations at high redshift. We consider if the offset is related to the AGN activities. The straightforward way is to study such offset, i.e. $\Delta \log \mathcal M_{\rm BH}$, as a function of \mbh\ and Eddington ratios, showing in Figure~\ref{fig:offset_vs_MBH_edd}. Interestingly, we visually see the trend that the offset turns to be larger with at value of \mbh. However, at higher Eddington ratio, the offset turns to be lower.
% {\color{red} Some interpretations need to be presented.}
%}
%\begin{figure*}
%\centering
%\begin{tabular}{c c}
%\subfloat[Offset of the \mbh-\smass\ relation as a function of \mbh.]
%{\includegraphics[height=0.5\textwidth]{fig/offset_vs_MBH.pdf}}&
%\subfloat[Offset of the \mbh-\smass\ relation as a function of Eddington ratio.]
%{\includegraphics[height=0.5\textwidth]{fig/offset_vs_Edd.pdf}}\\
%\end{tabular}
%\caption{\label{fig:offset_vs_MBH_edd} 
%Illustration of the offset for high-$z$ \mbh-\smass\ sample as a function of \mbh\ (left) and Eddington ratio (right).}
%\end{figure*} 
%

@@

\subsection{Systematic with different local anchor}
To compare our high-$z$ sample to the local relation, we adopt the local measurements by \citet{Ben++10, Bennert++2011, H+R04}. In the literature, other local sample have been measured which could also be considered as the local anchor. We note that different local samples have inconsistency which could change the result of the co-evolutions. To estimate this effect, we compare our local \mbh-\smass\ sample to the local ones by \citet{Kormendy13} (hereafter K13). We find that the \mbh-\smass\ measurements in K13 have a global $\sim+0.3$~dex offset to our local ones, and if adopted would totally erase the offset of $\Delta\log$\mbh\ for high redshift sample.

However, we also realize that the \mbh-\sigstar\ relations by K13 also have a $\sim$0.3~dex offset to the ones by \citet{Woo2010}. Note that it is the local \mbh-\sigstar\ relation by \citet{Woo2010} that is used to determine the virial coefficient for our active BHs. Thus, if adopting the K13's sample, the \mbh\ of all the AGN sample should be increased by $\sim$0.3~dex. As a result, the different local measurement would only affect the level of the \mbh\ globally to both local and high-$z$ sample, with the offset unchanged.

We thus conclude that, if adopt K13 sample, the inference of the high redshift $\Delta\log$\mbh\ would remain at the same level. However, this quick comparison of the local sample highlights the need of using the solid local baseline for the future studies (Bennert et al., in prep).
